Binary companions of red giant stars in \apogee\ \DR

### 2018-02-27 paper/1-catalog/twoface-catalog.tex
Some BS

Using the maximum-likelihood hyperparameters derived from the initial posterior
samplings (see \sectionname~\ref{sec:initsampling}), we update and fix the
excess variance prior distribution parameters---$(\mu_{y}, \sigma_{y}) = (9.5,
1.6)$ in units of $\textrm{m}~\textrm{s}^{-1}$---and re-run \thejoker\ on the
parent sample of \apogee\ \DR\ stars.
\todo{Discuss how this relates to empirical Bayes?}

From this run, 91,096 stars completed and successfully returned \nposterior\
samples using \thejoker\ alone.
The remaining 5,135 stars did not return \nposterior\ samples: 4,744 were
flagged as \emph{needs more prior samples}, 391 as \emph{needs MCMC}.

\todo{Stuff about full catalog of posterior samples, available online}

@@

>>>>

Using the maximum-likelihood hyperparameters derived from the initial posterior
samplings (see \sectionname~\ref{sec:inferjitter}), we update and fix the
excess variance prior distribution parameters---$(\mu_{y}, \sigma_{y}) = (9.5,
1.6)$, in units of $\textrm{m}~\textrm{s}^{-1}$---and re-run \thejoker\ on the
parent sample of \apogee\ \DR\ stars.
\todo{Discuss how this relates to empirical Bayes?}

From this run, 91,096 stars completed and successfully returned \nposterior\
samples using \thejoker\ alone.
The remaining 5,135 stars did not return \nposterior\ samples: 4,744 were
flagged as \emph{needs more prior samples}, 391 as \emph{needs MCMC}; We
continue generating samples for these stars using the methodology explained
above (see \sectionname~\ref{sec:samplings}).
In the end, \todo{XX} stars have completed samplings with \nposterior\ samples,
and, after re-running \thejoker\ with twice as many prior samples, \todo{XX}
stars still have fewer samples that are multi-modal in period.

The full catalog of posterior samples for all \apogee\ stars in our parent
sample is available online.
\todo{Structure of table, where to download, make a webpage with some
information?}

@@

We don't expect there to be a sharp transition in orbital parameters between
stars with companions and stars without companions: There is a continuum of
companion properties.
For example, the companion masses can be brown dwarf-like, or at long periods,
or at high inclination, all of which will make the velocity semi-amplitude, $K$,
small for a given system.
From the radial velocity data alone, there is therefore no way to select a
complete sample of stars with and without companions.
